\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-04 metatheory-condensed.tex
Phrasing
consistency

The definitive version is a \textbf{pen-and-paper} formalization assuming the facility of quotient inductive-inductive types~\cite{nordvall2010inductive,altkap2016} and extensional equality (equality reflection), available as a supplemental file in a \textbf{(pseudo-)Agda syntax}. Our formalization is directly following Agda syntax and type-checking (equality-checking) is done manually, leaving traces in the comments. We are currently working on mechanizing it and using Agda's rewriting mechanism to replace our limited application of equality reflection. 
%
We also typeset a more complete set of rules than
the space allows and present it in a supplemental appendix.
%
Another supplemental appendix gives a larger-scale example than
\cref{fig:stlc-linkage-typing} showing how families are modeled and
type-checked using linkages and linkage transformers.

>>>>

The definitive version is a \textbf{pen-and-paper} formalization assuming the facility of quotient inductive-inductive types~\cite{nordvall2010inductive,altkap2016} and extensional equality (equality reflection), available as a supplemental file in a \textbf{(pseudo-)Agda syntax}. Our formalization is directly following Agda syntax and type-checking (equality-checking) is done manually, leaving traces in the comments. We are currently working on mechanizing it and relying on Agda's rewriting mechanism to replace our limited usage of equality reflection. 
%
We also typeset a more complete set of rules than
the space allows and present it in a supplemental appendix.
%
Another supplemental appendix gives a more complete example than
\cref{fig:stlc-linkage-typing} showing how families are modeled and
type-checked using linkages and linkage transformers.
